A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-06-23 LensingPaper_draft_v4.01.tex
Edited part of the Future Work and Central kinematics section in the Discussion.

\Wilma{[TO DO: Mention somewhere else: "Overall, we were not able to find a consistent explanation for J1331's central $v_\text{rms}$ dip. It cannot be due to tangential velocity anisotropy in the center alone (see Section \ref{sec:results_JAM_SB_MfL}, Figure \ref{fig:JAM_modelA2}). It also cannot be explained by a strong contribution of DM inside the bulge together with a moderate tagential velocity anisotropy, because the corresponding \NEW{NFW} DM halo\OLD{s} would still be too massive to fit the data in the outer regions (see Section \ref{sec:results_JAM_NFW}, Figure \ref{fig:modelB4_vrms})."]}

@@

\Wilma{[TO DO: The referee says: "In Section 5.2, the authors could make suggestions for what might be causing the two
$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
more convincing suggestions – e.g. could it be associated with the possible recent
merger that is explored in Section 5.3? It would be more satisfying if some
suggestions like this could be put forward."]}

@@

%--------------------------------------------
\subsection{Future work}
%--------------------------------------------
\Wilma{[TO DO: Go through it and make it shorter.]}
%--------------------------------------------
Standard JAM modelling approaches seem not to work for J1331. The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.

2-dimensional stellar kinematics would greatly help to resolve this problem. The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331. High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure. High spectral resolution would be important to be able to reliably measure the low velocity dispersion in the outer regions of J1331.

Specifically 2D kinematics should help to answer the following questions: Is the drop in $v_\text{rms}$ around $R' \sim 3-6~\text{kpc}$ real? Did the long slit spectrograph maybe miss the major axis of the disk? And most importantly: Are the kinematics asymmetric? Is it possible that there even exists a kinematic twist due to the merger in J1331's past?

>>>>

@@

@@

%--------------------------------------------
\subsection{Future work}
%--------------------------------------------

%--------------------------------------------
\OLD{Standard JAM modelling approaches seem not to work for J1331. The existing data---photometry and major axis kinematics---is however not sufficient to decide which of our model assumptions lead to the failure to find an overall consistent mass model.}
\NEW{J1331's merging history and peculiar kinematics make it a valuable and exiting target to study merger remnants and a challenge for dynamical modelling techniques. We found however that the existing data alone---photometry and major axis kinematics---is not sufficient to resolve all the ambiguities we encountered in our modelling.}

\OLD{2-dimensional stellar kinematics would greatly help to resolve this problem. }The main future work would be therefore getting high-resolution integral-field spectroscopy for J1331. High spatial resolution would be required to clearly identify J1331's presumably complex kinematic structure. High spectral resolution would be important to be able to reliably measure the low velocity dispersion in the outer regions of J1331.

Specifically 2D kinematics should help to answer the following questions: Is the drop in $v_\text{rms}$ around $R' \sim 3-6~\text{kpc}$ real? Did the long slit spectrograph maybe miss the major axis of the disk? And most importantly: Are the kinematics asymmetric? Is it possible that there even exists a kinematic twist due to the merger in J1331's past? \NEW{In the latter two cases we would need to apply non-axisymmetric Jeans models to J1331 as the assumption of axisymmetry of this work would not be valid anymore.}
